---
title: "Reviewing your activity"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(rjson)
data <- fromJSON(file = "tracking_data.json")
```

## Product interest

```{r interest1}
category_scores <- sapply(data$gaze, function(category) {
  items <- unlist(category)
  
  # to determine which categories to show to the participant, calculate a score combining total time and range of times spent looking at objects within categories
  return(sum(items) + max(items) - min(items))
})

sorted_categories <- names(sort(category_scores, decreasing = TRUE))
items <- unlist(data$gaze[[sorted_categories[1]]])

interest <- tibble(item = names(items), time = items)

interest %>%
  mutate(item = fct_reorder(item, desc(time))) %>%
  ggplot() +
  geom_col(aes(x = item, y = time)) +
  labs(title = paste("Gaze tracking:", sorted_categories[1])) +
  xlab("") +
  ylab("Time (sec)") +
  theme_bw()
```

Based on what you looked at the most, Total VR has inferred that you are interested in `r names(sort(items, decreasing = TRUE))[1]`.

## Cognitive processing speed
```{r reaction, out.width="80%"}
baseline = 1.55

# if a reaction was observed; should probably later change this to having the properties be absent from the JSON and checking for length > 0, but I ran into issues with that (I suspect because the optional property was messing up serialization)
if(data$`reaction times`$cat > 0)
{
  user_time <- mean(unlist(data$`reaction times`))
  
  reaction <- tibble(item = c("Baseline", "Your average time"), time = c(baseline, user_time))

  reaction %>%
    ggplot() +
    geom_col(aes(x = item, y = time)) +
    labs(title = "Reaction time") +
    xlab("") +
    ylab("Reaction time (sec)") +
    theme_bw()
}
```

`r ifelse(!length(data$"reaction times"), "No relevant data collected.", paste("Based on your reactions to things happening around you, Total VR has inferred that your cognitive processing speed is likely", ifelse(user_time > 1.2 * baseline, "below", ifelse(user_time < 0.8 * baseline, "above", "about")), "average."))`

## Product interest

```{r interest2}
items <- unlist(data$gaze[[sorted_categories[2]]])

interest <- tibble(item = names(items), time = items)

interest %>%
  mutate(item = fct_reorder(item, desc(time))) %>%
  ggplot() +
  geom_col(aes(x = item, y = time)) +
  labs(title = paste("Gaze tracking:", sorted_categories[2])) +
  xlab("") +
  ylab("Time (sec)") +
  theme_bw()
```

Based on what you looked at the most, Total VR has inferred that you are interested in `r names(sort(items, decreasing = TRUE))[1]`.

## Product interest

```{r interest3}
items <- unlist(data$gaze[[sorted_categories[3]]])

interest <- tibble(item = names(items), time = items)

interest %>%
  mutate(item = fct_reorder(item, desc(time))) %>%
  ggplot() +
  geom_col(aes(x = item, y = time)) +
  labs(title = paste("Gaze tracking:", sorted_categories[3])) +
  xlab("") +
  ylab("Time (sec)") +
  theme_bw()
```

Based on what you looked at the most, Total VR has inferred that you are interested in `r names(sort(items, decreasing = TRUE))[1]`.

## Political leaning

```{r politics, out.width="80%"}
liberal_correlative_names <- c("rap", "reggae", "EDM", "hybrid vehicles")
liberal_correlatives <- c(data$gaze$music$`rap`, data$gaze$music$`reggae`, data$gaze$music$`EDM`, data$gaze$cars$`hybrid vehicles`)
conservative_correlative_names <- c("country", "oldies", "pickup trucks")
conservative_correlatives <- c(data$gaze$music$`country`, data$gaze$music$`oldies`, data$gaze$cars$`pickup trucks`)

leaning <- tibble(item = c("Liberal correlative index", "Conservative correlative index"), partisan_lean = 100 * c(mean(liberal_correlatives), mean(conservative_correlatives)))

leaning %>%
  ggplot() +
  geom_col(aes(x = item, y = partisan_lean)) +
  labs(title = "Political leaning") +
  xlab("") +
  ylab("Partisan lean") +
  theme_bw()

if(mean(liberal_correlatives) > mean(conservative_correlatives))
{
  label <- "liberal"
  explanation <- liberal_correlative_names[which(liberal_correlatives == max(liberal_correlatives))]
} else
{
  label <- "conservative"
  explanation <- conservative_correlative_names[which(conservative_correlatives == max(conservative_correlatives))]
}
```

Based on what you looked at the most, Total VR has inferred that you lean `r label` politically. The most impactful factor was your inferred interest in `r explanation`.
